---
title: "Species Profile"
header-includes:
  - \usepackage{caption}
  - \captionsetup{font = LARGE}
  - \captionsetup[table]{skip=1pt} 
  - \usepackage{placeins}
  - \usepackage{colortbl}
  - \usepackage{array}
output: 
  pdf_document: 
    keep_tex: yes
classoption: x11names
---

\FloatBarrier

```{r echo=FALSE}
index <- which(species_library$common_name == CurrentSpeciesName, arr.ind = TRUE)
sname <- species_library$common_name[index]
scname <- species_library$scientific_name[index]
```

\begin{center}

\begingroup
\LARGE 

 `r paste(sname," (",scname, ")" ,sep = "")`

 Visual Species Profile

 FishToxTranslator `r packageVersion("FishToxTranslator")`

 Generated: `r format(Sys.time(), '%m/%d/%Y')`
 
\endgroup

\end{center}

\vspace{-2cm}

\FloatBarrier

```{r echo=FALSE}
cSDO <- as.character(species_library$parameter_data[which(species_library$common_name==sname)])
cLHP <- get(cSDO)
dfs <<- FishToxTranslator::TemplateToParameters(cLHP)
```

\begin{center}
```{r, echo=FALSE}
zhatch <- format_number(dfs$z_hatch[1])
zinf <- format_number(dfs$z_inf[1])
kg <- format_number(dfs$k_g[1])
varkg <- format_number(dfs$var_k_g[1])
vareg <- format_number(dfs$var_e_g[1])
alloslope <- format_number(dfs$allo_slope[1])
allointercept <- format_number(dfs$allo_intercept[1])

dfnew1 <- data.frame(Value = c(zhatch, zinf, kg, varkg, vareg, alloslope, allointercept), Name = c(parameters_master[["name"]][parameters_master$id == "z_hatch"], parameters_master[["name"]][parameters_master$id == "z_inf"], parameters_master[["name"]][parameters_master$id == "z_hatch"], parameters_master[["name"]][parameters_master$id == "var_k_g"], 
parameters_master[["name"]][parameters_master$id == "var_e_g"],
parameters_master[["name"]][parameters_master$id == "allo_slope"],
parameters_master[["name"]][parameters_master$id == "allo_slope"]))

dfnew1 %>%
  kbl(format = "latex", align = "l", booktabs = FALSE, vline = "", caption = "Growth Parameters") %>%
  kable_styling(font_size = 16) %>%
  row_spec(row = 0, bold = TRUE, italic = FALSE) %>%
  row_spec(row = 2, background = "Snow3") %>%
  row_spec(row = 4, background = "Snow3") %>%
  row_spec(row = 6, background = "Snow3") %>%
  kableExtra::column_spec(column = 1, border_left = TRUE, width = "3.5em") %>%
  kableExtra::column_spec(column = 2, border_right = TRUE, width = "14em") 
```
\end{center}

\FloatBarrier

```{r,  echo=FALSE}
FishToxTranslator::PlotGrowth(forProfile = TRUE, species = sname)
```

\FloatBarrier

```{r, echo=FALSE, warnings=FALSE, message=FALSE,fig.align='right'}
FishToxTranslator::PlotGrowthTrajectory(species = sname)
```

\FloatBarrier

```{r, echo=FALSE, fig.align='right', warning=FALSE, warnings=FALSE}
FishToxTranslator:::PlotSurvivalTrajectory(species = sname)
```

\FloatBarrier


```{r, echo=FALSE, fig.align='right'}
FishToxTranslator::PlotLengthToMass(species = sname)
```

\FloatBarrier

\begin{center}
```{r, echo=FALSE}
smin <- format_number(dfs$s_min[1])
smax <- format_number(dfs$s_max[1])
sa <- format_number(dfs$s_a[1])
sb <- format_number(dfs$s_b[1])
psmort <- format_number(dfs$post_spawning_mortality[1])

dfnew2 <- data.frame(Value = c(smin, smax, sa, sb, psmort), Name = c(parameters_master[["name"]][parameters_master$id == "s_min"], parameters_master[["name"]][parameters_master$id == "s_max"], parameters_master[["name"]][parameters_master$id == "s_a"], parameters_master[["name"]][parameters_master$id == "s_b"], 
parameters_master[["name"]][parameters_master$id == "post_spawning_mortality"]))

dfnew2 %>%
  kbl(format = "latex", align = "l", booktabs = FALSE, vline = "", caption = "Survival Parameters") %>%
  kable_styling(font_size = 16) %>%
  row_spec(row = 0, bold = TRUE, italic = FALSE) %>%
  row_spec(row = 2, background = "Snow3") %>%
  row_spec(row = 4, background = "Snow3") %>%
  kableExtra::column_spec(column = 1, border_left = TRUE, width = "3.5em") %>%
  kableExtra::column_spec(column = 2, border_right = TRUE, width = "14em") 
```
\end{center}

\FloatBarrier

```{r,  echo=FALSE}
FishToxTranslator::PlotSurvival(forProfile = TRUE, species = sname)
```
\FloatBarrier

\begin{center}
```{r, echo=FALSE}
zrepro <- format_number(dfs$z_repro[1])
sexratio <- format_number(dfs$sex_ratio[1])
fecuslope <- format_number(dfs$fecu_slope[1])
fecuintercept <- format_number(dfs$fecu_intercept[1])
hatchrate <- format_number(dfs$hatch_rate[1])
pawnint <- format_number(dfs$spawn_int[1])
spawnsmaxseason <- format_number(dfs$spawns_max_season[1])
reprostart <- format_number(dfs$repro_start[1])
reproend <- format_number(dfs$repro_end[1])

dfnew3 <- data.frame(Value = c(zrepro, sexratio, fecuslope, fecuintercept, hatchrate, pawnint, spawnsmaxseason, reprostart, reproend), Name = c(parameters_master[["name"]][parameters_master$id == "z_repro"], parameters_master[["name"]][parameters_master$id == "sex_ratio"], parameters_master[["name"]][parameters_master$id == "fecu_slope"], parameters_master[["name"]][parameters_master$id == "fecu_intercept"], parameters_master[["name"]][parameters_master$id == "hatch_rate"], parameters_master[["name"]][parameters_master$id == "spawn_int"], parameters_master[["name"]][parameters_master$id == "spawns_max_season"], parameters_master[["name"]][parameters_master$id == "repro_start"], parameters_master[["name"]][parameters_master$id == "repro_end"]))

dfnew3 %>%
  kbl(format = "latex", align = "l", booktabs = FALSE, vline = "", caption = "Reproduction Parameters") %>%
  kable_styling(font_size = 16) %>%
  row_spec(row = 0, bold = TRUE, italic = FALSE) %>%
  row_spec(row = 2, background = "Snow3") %>%
  row_spec(row = 4, background = "Snow3") %>%
  row_spec(row = 6, background = "Snow3") %>%
  row_spec(row = 8, background = "Snow3") %>%
  kableExtra::column_spec(column = 1, border_left = TRUE, width = "3.5em") %>%
  kableExtra::column_spec(column = 2, border_right = TRUE, width = "14em")
```
\end{center}

\FloatBarrier

```{r, echo=FALSE}
FishToxTranslator::PlotReproduction(forProfile = TRUE, species = sname)
```
